Data Visualization

### 2023-01-30 src/data_viz.Rmd
started bar chart

```{r}
total_scores_data <- read_sheet("https://docs.google.com/spreadsheets/d/1yqjhJvXUcEiC3qiYWkKNlF6NNpYXWg15zZHwmwpS5Q0/edit#gid=1307699202")

@@

>>>>

```{r}
total_score_data <- read_sheet("https://docs.google.com/spreadsheets/d/1yqjhJvXUcEiC3qiYWkKNlF6NNpYXWg15zZHwmwpS5Q0/edit#gid=1307699202") %>% 
  rename(financial_score = normalized_irr,
         climate_impact = inverted_n_total_co2,
         health_impact = inverted_n_health_emissions_cost,
         electricity = normalized_annual_renewable,
         climate_risk = normalized_inverted_climate_risk)

@@

```{r}
score_tidy <- total_score_data %>% 
  pivot_longer(cols = c(real_estate_score, landlord_score, financial_score:climate_risk),
               names_to = "criteria",
               values_to = "criteria_score") %>% 
  filter(city_msa != "Portland") %>% 
  group_by(city_msa)

```{r}
ggplot(data = score_tidy, aes(y = city_msa, x = total_score_owen, fill = criteria)) + 
    geom_bar()

ggplot(data = score_tidy, aes(y = city_msa, x = total_score_owen, fill = criteria)) + 
    geom_col(position="stacked")
```
